---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RARchitect

<!-- badges: start -->
<!-- badges: end -->

A framework for simulating Response-Adaptive Randomization (RAR) 
clinical trial designs for different types of outcomes. Its purpose is to 
assist researchers and statisticians in designing RAR trials by allowing them 
to test various configurations and parameters, such as prior settings, 
allocation tuning and clipping strategies, and recruitment rates, through simulations.

## Installation

You can install the development version of RARchitect from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("StinaZet/RARchitect")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(RARchitect)
# Simulate a Binary Outcome Trial
# Example 1: Simulate a Binary Outcome Trial
set.seed(101)
results_binary <- simulate_brar_trial(
 outcome_type = "binary",
 distribution = "bernoulli",
 arms = 2, N = 100, blocksize = 10,
 modelpar = c(0.6, 0.4),
 priors = matrix(c(1, 1, 1, 1), nrow = 2, byrow = TRUE),
 tuning = 1, clipping = 0, burnin = 0, randmethod = "coin",
 postprobmethod = "exact", # Or "simulation"
 recruitment_rate = 5,
 observation_delay = 30)
head(results_binary)

# Example 2: Simulate a Normal Outcome Trial
set.seed(102)
model_params_norm <- matrix(c(10, 8, 2, 2), nrow = 2, byrow = TRUE)
prior_params_norm <- matrix(c(0, 0, 1, 1), nrow = 2, byrow = TRUE)

results_normal <- simulate_brar_trial(
 outcome_type = "cont",
 distribution = "normal",
 arms = 2, N = 200, blocksize = 10, known_var = TRUE,
 priors = prior_params_norm,
 modelpar = model_params_norm,
 tuning = 1, clipping = 0, burnin = 10, randmethod = "urn",
 postprobmethod = "exact", # Or "simulation"
 recruitment_rate = 10,
 observation_delay = 15)
head(results_normal)

# Example 3: Simulate an Exponential Outcome Trial
# True rates for arms: lambda1 = 0.2 (mean = 5), lambda2 = 0.1 (mean = 10)
set.seed(105)
prior_params_exp <- matrix(c(1, 1, 1, 1), nrow = 2, byrow = TRUE) # Gamma(1,1) priors
true_rates_exp <- c(0.2, 0.1)

results_exponential <- simulate_brar_trial(
 outcome_type = "cont",
 distribution = "exponential",
 arms = 2, N = 120, blocksize = 1,
 priors = prior_params_exp,
 modelpar = true_rates_exp,
 tuning = 1, clipping = 0, burnin = 0,
 randmethod = "coin",
 postprobmethod = "simulation",
 recruitment_rate = 6,
 observation_delay = 5)
head(results_exponential)
```


